r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-10-26 r-package/paper2020/paper2020.Rmd
adds plot showing travel time distribution to paper

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

@@

The first step when using r5r is to set the amount of memory available to Java. 
By default `R` allocates only 512 MB of memory for Java processes~~, which is not 
enough for large queries using r5r~~. To increase available memory to 2GB, for 
example, we need to set the `java.parameters` option at the beginning of the 
script as follows:

@@

```{r, message = FALSE}
time_window <- 60
percentiles <- c(25, 50, 75)

@@

@@

```{r, message = FALSE, fig.width = 7, fig.height = 5}
# extract OSM network
street_net <- street_network_to_sf(r5r_core)

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7, 
  fig.height = 5
)

@@

The first step when using r5r is to set the amount of memory available to Java. 
By default `R` allocates only 512 MB of memory for Java processes. To increase 
available memory to 2GB, for example, we need to set the `java.parameters` 
option at the beginning of the script as follows:

@@

```{r, message = FALSE}
time_window <- 120
percentiles <- c(25, 50, 75)

@@

The image below depicts the travel time distribution for each origin/destination in which a trip could be completed within the specified parameters. The pairs are ordered in the x axis by their median travel time and each point in the plot area pictures a distinct distribution percentile.

```{r, message = FALSE}
order_data <- ttm[, .(fromId, toId, travel_time_p025, travel_time_p050, travel_time_p075)]
order_data <- order_data[order(travel_time_p050, travel_time_p025, travel_time_p075)]
id_order   <- order_data[, id := paste0(fromId, "_", toId)]$id

pctls <- paste0("travel_time_p", formatC(percentiles, width = 3, flag = "0"))

plot_data <- melt(ttm, measure = pctls, variable = "percentil", value = "travel_time")
plot_data[, percentil := as.integer(regmatches(percentil, regexpr("\\d+", percentil)))]
plot_data[, travel_time := fifelse(travel_time > max_trip_duration, NA_integer_, travel_time)]
plot_data[, id := factor(paste0(fromId, "_", toId), levels = id_order)]

ggplot(plot_data) + 
   geom_point(aes(id, travel_time, color = percentil), alpha = 0.1, size = 1) + 
   theme_minimal() +
   theme(axis.title.x = element_blank(), axis.text.x = element_blank())
```

Notice that the leftmost origin/destination pairs do not exhibit any variation in the distribution of their travel time along the time window. This is because the trips between such pairs rely solely on walking to be completed, therefore are not susceptible to transit reliability issues.

@@

```{r, message = FALSE}
# extract OSM network
street_net <- street_network_to_sf(r5r_core)
